R code for 'Apparent physiological costs of blood parasite infection in the early-life of a vertebrate host - only in highest infections

### 2022-09-19 MS_physiology_infection.Rmd
Add files via upload

Fig_4C = ggplot(mod_bc_para) + 
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted) + 
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc_para$lower_CI, ymax = mod_bc_para$higher_CI),
                colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bc_para$predicted - mod_bc_para$se,
                    ymax = mod_bc_para$predicted + mod_bc_para$se),
                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),  
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 5, yend = 60)) + 
    geom_text(aes(x = 3, y = 67),
              label = "t = -1.76, df = 247, P = 0.080", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 1, yend = 53)) + 
  geom_segment(size = .8,
                 aes(x = 5, y = 60, xend = 5, yend = 53))
```

@@

# Plotting predicted values across infection intensities
## -----------------------------------------------------------------------------
Fig_4D = ggplot(mod_gr_para) + 
  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted) + 
  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_errorbar(aes(ymin = mod_gr_para$lower_CI,
                    ymax = mod_gr_para$higher_CI), colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_gr_para$predicted - mod_gr_para$se,
                    ymax = mod_gr_para$predicted + mod_gr_para$se),size = 8, 
                colour = wes_palette("Zissou1",5), width = 0) + 
  geom_point(color = "black", outlier.shape = NA, size = 4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
               aes(x = 1, y = 30, xend = 5, yend = 30)) + 
  geom_text(aes(x = 3, y = 31),
            label = "t = 2.06, df = 258, P = 0.094", size = 5) + 
  geom_segment(size = .8,
               aes(x = 1, y = 29, xend = 1, yend = 30)) + 
  geom_segment(size = .8,
               aes(x = 5, y = 29, xend = 5, yend = 30))
```

@@

Fig_S3C = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,delta_body_condition) + 
  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "\U0394 Body condition") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5, show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

Fig_S3D = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,Growth_rate) + 
  geom_hline(yintercept = mean(df$Growth_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8, width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5, show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20), 
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

@@

## Plotting effect sizes of 'infection intensities' models
## ----------------------------------------------------------------------------- 
Fig_S5A = plot_model(
  lmer_br_para,
  sort.est = T,
  se = T,
  title = "Breathing rate",
  axis.labels = 
    rev(c("Infection intensity [2] : Treatment [Malarone]","Age (days)",
          "Infection intensity 1", "Infection intensity 4",
          "Infection intensity [1] : Treatment [Malarone]",
          "Infection intensity [3] : Treatment [Malarone]",
          "Infection intensity [0] : Treatment [Malarone]",
          "Sex [Males]","Infection intensity 3","Sampling interval",
          "Infection intensity 2","Weight (g)","Ambient temperature",
          "Year [2019]","Year [2018]","Year [2020]")))

Fig_S5B = plot_model(
  lmer_bt_para,
  sort.est = T,
  se = T,
  title = "Body temperature",
  axis.labels = 
    rev(c("Ambient temperature","Year [2020]","Age (days)",
          "Infection intensity [3] : Treatment [Malarone]",
          "Infection intensity 1", "Infection intensity [2] : Treatment [Malarone]",
          "Weight (g)","Infection intensity 2","Sex [Males]",
          "Infection intensity [0] : Treatment [Malarone]",
          "Infection intensity [1] : Treatment [Malarone]",
          "Infection intensity 3", "Sampling interval","Infection intensity 4")))

Fig_S5C = plot_model(
  lmer_bc_para,
  sort.est = T,
  se = T,
  title = "\U0394 Body condition",
  axis.labels = 
    rev(c("Year [2020]","Year [2018]","Year [2019]",
          "Infection intensity [2] : Treatment [Malarone]",
          "Infection intensity 1","Sampling interval",
          "Infection intensity [3] : Treatment [Malarone]",
          "Infection intensity [0] : Treatment [Malarone]",
          "Age (days)","Sex [Males]","Infection intensity 3",
          "Infection intensity 2","Infection intensity [1] : Treatment [Malarone]",
          "Infection intensity 4")))

Fig_S5D = plot_model(
  lmer_gr_para,
  sort.est = T,
  se = T,
  title = "Growth rate", 
  axis.labels = 
    rev(c("Year [2020]","Infection intensity [2] : Treatment [Malarone]",
          "Year [2018]","Year [2019]","Sampling interval","Infection intensity 1",
          "Infection intensity [3] : Treatment [Malarone]",
          "Infection intensity [0] : Treatment [Malarone]",
          "Infection intensity 3","Sex [Males]","Infection intensity 2",
          "Age (days)","Infection intensity 4","Infection intensity [1] : Treatment [Malarone]")))

>>>>

Fig_4C = ggplot(mod_bc_para) + 
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted) + 
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "Parasitemia", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc_para$lower_CI, ymax = mod_bc_para$higher_CI),
                colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bc_para$predicted - mod_bc_para$se,
                    ymax = mod_bc_para$predicted + mod_bc_para$se),
                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 20),  
        axis.title.x = element_text(size = 20, vjust=-0.5),
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 5, yend = 60)) + 
    geom_text(aes(x = 3, y = 67),
              label = "t = -1.76, df = 247, P = 0.080", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 60, xend = 1, yend = 53)) + 
  geom_segment(size = .8,
                 aes(x = 5, y = 60, xend = 5, yend = 53))
```

@@

# Plotting predicted values across infection intensities
## -----------------------------------------------------------------------------
Fig_4D = ggplot(mod_gr_para) + 
  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted) + 
  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "Parasitemia", y = "Growth rate") + 
  geom_errorbar(aes(ymin = mod_gr_para$lower_CI,
                    ymax = mod_gr_para$higher_CI), colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_gr_para$predicted - mod_gr_para$se,
                    ymax = mod_gr_para$predicted + mod_gr_para$se),size = 8, 
                colour = wes_palette("Zissou1",5), width = 0) + 
  geom_point(color = "black", outlier.shape = NA, size = 4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20),
        axis.title.x = element_text(size = 20, vjust=-0.5),
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
               aes(x = 1, y = 30, xend = 5, yend = 30)) + 
  geom_text(aes(x = 3, y = 31),
            label = "t = 2.06, df = 258, P = 0.094", size = 5) + 
  geom_segment(size = .8,
               aes(x = 1, y = 29, xend = 1, yend = 30)) + 
  geom_segment(size = .8,
               aes(x = 5, y = 29, xend = 5, yend = 30))
```

@@

Fig_S3C = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,delta_body_condition) + 
  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
  labs(x = "Parasitemia", y = "\U0394 Body condition") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5, show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 16), 
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

Fig_S3D = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
  aes(Infection_intensity.2,Growth_rate) + 
  geom_hline(yintercept = mean(df$Growth_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "Parasitemia", y = "Growth rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size = 2.8, width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size = 5, show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 20), 
        axis.text = element_text(size = 16),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

@@

## Plotting effect sizes of 'infection intensities' models
## ----------------------------------------------------------------------------- 
Fig_S5A = plot_model(
  lmer_br_para,
  sort.est = T,
  se = T,
  title = "Breathing rate",
  axis.labels = 
    rev(c("Parasitemia [2] : Treatment [Malarone]","Age (days)",
          "Parasitemia 1", "Parasitemia 4",
          "Parasitemia [1] : Treatment [Malarone]",
          "Parasitemia [3] : Treatment [Malarone]",
          "Parasitemia [0] : Treatment [Malarone]",
          "Sex [Males]","Parasitemia 3","Sampling interval",
          "Parasitemia 2","Weight (g)","Ambient temperature",
          "Year [2019]","Year [2018]","Year [2020]")))

Fig_S5B = plot_model(
  lmer_bt_para,
  sort.est = T,
  se = T,
  title = "Body temperature",
  axis.labels = 
    rev(c("Ambient temperature","Year [2020]","Age (days)",
          "Parasitemia [3] : Treatment [Malarone]",
          "Parasitemia 1", "Parasitemia [2] : Treatment [Malarone]",
          "Weight (g)","Parasitemia 2","Sex [Males]",
          "Parasitemia [0] : Treatment [Malarone]",
          "Parasitemia [1] : Treatment [Malarone]",
          "Parasitemia 3", "Sampling interval","Parasitemia 4")))

Fig_S5C = plot_model(
  lmer_bc_para,
  sort.est = T,
  se = T,
  title = "\U0394 Body condition",
  axis.labels = 
    rev(c("Year [2020]","Year [2018]","Year [2019]",
          "Parasitemia [2] : Treatment [Malarone]",
          "Parasitemia 1","Sampling interval",
          "Parasitemia [3] : Treatment [Malarone]",
          "Parasitemia [0] : Treatment [Malarone]",
          "Age (days)","Sex [Males]","Parasitemia 3",
          "Parasitemia 2","Parasitemia [1] : Treatment [Malarone]",
          "Parasitemia 4")))

Fig_S5D = plot_model(
  lmer_gr_para,
  sort.est = T,
  se = T,
  title = "Growth rate", 
  axis.labels = 
    rev(c("Year [2020]","Parasitemia [2] : Treatment [Malarone]",
          "Year [2018]","Year [2019]","Sampling interval","Parasitemia 1",
          "Parasitemia [3] : Treatment [Malarone]",
          "Parasitemia [0] : Treatment [Malarone]",
          "Parasitemia 3","Sex [Males]","Parasitemia 2",
          "Age (days)","Parasitemia 4","Parasitemia [1] : Treatment [Malarone]")))
